On Developing User Interfaces for Piloting Unmanned Systems

### 2014-02-13 Papers/RSN2014/paper.tex
* Updating paper

As unmanned aerial vehicles and ground robots become less expensive and more
pervasive, the need for intuitive control interfaces for multiple distributed
systems in environments such as search-and-rescue, resource exploration, and
other situations becomes more pronounced. However, current generations of
interfaces for controlling multiple unmanned systems focus on micro-manipulation
of individual systems within a swarm of autonomous entities. For instance, an
interface for such a grouping of systems may require an operator to select one
or more entities and give them a proximate waypoint, often via GPS, to move to.
Examples of existing systems that do this include the AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner; and AFRL's ATAK mission planning environment~\cite{gillen2012beyond}.
These concepts are extended further in 3D piloting systems based on landmark
navigation~\cite{ranft20133d} and augmented reality~\cite{kochflying}, as
these interfaces tend to require the full attention
of an operator on each UAS, rather than focusing on the group operations.

@@

To understand the benefits of the GAMS interfaces, we must first explore some
of the problems with the state-of-the-art. In this section, we describe some
simple, repeatable experiments with waypoint navigation systems, which as
mentioned in Section~\ref{sec:introduction} are
used in software like AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner; and AFRL's ATAK mission planning environment~\cite{gillen2012beyond}.

@@

In this paper, we have discussed insights into research conducted in the Group
Autonomy for Mobile Systems project at Carnegie Mellon University in regards
to user interfaces for swarms of unmanned autonomous systems. The interfaces
and coupled artificial intelligence discussed here are available as open source at
http://gams-cmu.googlecode.com. Future work on this project is directed toward
using these interfaces to direct dozens of UAS to perform complex mission tasks
for search-and-rescue, agriculture, border patrol, and other tasks.

>>>>

As unmanned aerial vehicles and ground robots become less expensive and more
pervasive, the need for intuitive control interfaces for multiple distributed
systems in environments such as search-and-rescue, resource exploration, and
other situations becomes more pronounced. However, current generations of
interfaces for controlling multiple unmanned systems focus on micro-manipulation
of individual systems within a swarm of autonomous entities. For instance, an
interface for such a grouping of systems may require an operator to select one
or more entities and give them a proximate waypoint, often via GPS, to move to.
Examples of existing systems that do this include the AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner~\cite{arora2013development}; and AFRL's ATAK mission
planning environment~\cite{gillen2012beyond}.
These concepts are extended further in 3D piloting systems based on landmark
navigation~\cite{ranft20133d} and augmented reality~\cite{kochflying}, as
these interfaces tend to require the full attention
of an operator on each UAS, rather than focusing on the group operations.

@@

To understand the benefits of the GAMS interfaces, we must first explore some
of the problems with the state-of-the-art. In this section, we describe some
simple, repeatable experiments with waypoint navigation systems, which as
mentioned in Section~\ref{sec:introduction} are
used in software like AR.Drone 2.0 Free Flight
Flight Recorder Application~\cite{irizarry2012usability};
the 3D Robotics Mission Planner, Droid Planner,
APM Planner~\cite{arora2013development}; and AFRL's ATAK mission planning
environment~\cite{gillen2012beyond}.

@@

In this paper, we have discussed insights into research conducted in the Group
Autonomy for Mobile Systems project at Carnegie Mellon University in regards
to user interfaces for swarms of unmanned autonomous systems. The user
interfaces developed and showcased here have been shown to decrease
user actions required and also reduce error by relying on autonomy within
the devices to cover areas correctly. Future work on this project is directed toward
using these interfaces to direct dozens of UAS to perform complex mission tasks
for search-and-rescue, agriculture, border patrol, and other tasks.

All interfaces and code are available as open source at
http://gams-cmu.googlecode.com.
